---
title: "Reliability of continuous skin and body temperature measurement using a wireless wearable thermometer in a surgical inpatient unit"
author:
  - name: "Wojciech Francuzik"
    email: wojciech.francuzik@medigent.org
    institute: [Charite]
    correspondence: false
    equal_contributor: true
  - name: "Paweł Prociów"
    email: prociow@gmail.com
    institute: [Ins1]
    correspondence: false
    equal_contributor: true
  - name: "Tomasz Banasiewicz"
    email: tbanasiewicz@op.pl
    institute: [Ins2]
    correspondence: false
    equal_contributor: true
institute:
  - Charite: "Charité – Universitätsmedizin Berlin, corporate member of Freie Universität Berlin and Humboldt-Universität zu Berlin, Division of Allergy and Immunology, Department of Dermatology, Venereology and Allergology, Charitéplatz 1, 10117 Berlin, Germany"
  - Ins1: "Afiliacja Pawła"
  - Ins2: "Afiliacja Tomka"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

<!-- With the following code you can access and display values from the yml header above. -->

Keywords: `r rmarkdown::metadata$keywords`

Highlights: `r rmarkdown::metadata$highlights`

<!-- The following code chunk defines some general settings how code chunks should behave. -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)
```

<!-- The actual document text starts here: -->

# Introduction

## Clinical need for temperature measurement in surgical patients 

## Background for continous temperature measurement in clinical situations

## Aim:
To investigate the measurement error of the Warmie sensor compared to a reference thermometer.
Variables considered in the study: sensor location, user age, user gender

# Methods

## Data collection: 

## Gathered during the WTM-2020 study, 

## exported from RedCap, and organized for 

## analysis.



# Results

## Descriptive Analysis

### Information on the number of groups randomized, chosen based on the location of the sensor on the body

### Comparison of Warmie sensor measurements

### Analysis of observations from 48 patients

### Comparison of point measurements of the reference thermometer with the average of Warmie measurements

### Analysis of measurement error depending on age and sensor location

### Median calculation for measurement differences between devices.

### Application of calibration to improve measurement stability.

### Results: No significant improvement in measurement stability for chest, thigh, or wrist placements.

### Significant reduction in median error for measurements near the inner arm.

### Increase in variance observed for measurements near the armpit, indicating reduced stability.


### Suggested temperature adjustment

####  Improvement in measurement accuracy
#### Standard deviation of all observations
#### Reduction in standard deviation after transformations

# Discussion

##  Discussion of the average error per patient

## Why is the readout correction necessary?

## literature review of other methods

# Conclusion

Best location for the Warmie sensor for measurement stability
Possible adjustment of Warmie results and approximation of real temperature
Error distribution with estimated standard deviation

# Acknowledgements
The device was provided by the company Warmie. The company had no influence on the study design, data collection, analysis, or interpretation of the results. The authors would like to thank the study nurses for their support in data collection.

Wojciech Francuzik is the founder of Medigent and Warmie, and has a financial interest in the company. The other authors declare no conflict of interest.


# Do usunięcia (zostwiam na razie dla przykładu) 

\newpage

# References 

<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->

<div id="refs"></div>

\newpage


<!-- Here's some example analysis code: -->

```{r get-data, eval = FALSE}
# Note the path that we need to use to access our data files when rendering this document
my_data <- read.csv(here::here('analysis/data/raw_data/my_csv_file.csv'))
```

```{r demo-plot, fig.cap="A plot of random numbers"}
plot(rnorm(10))
```

Figure \@ref(fig:demo-plot) shows how we can have a caption and cross-reference for a plot

```{r demo-inline-code}
x <- round(pi, 2)
```

Here is an example of inline code `r x` in the middle of a sentence. 

# Discussion

# Conclusion


<!-- The following line inserts a page break  -->


### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies: 

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
